Programming Language Foundations in Agda

### 2019-07-01 papers/scp/PLFA.tex
Updated .gitignore; rewrote SCP paper to use elsarticle class

%\documentclass[runningheads,oribibl]{llncs}
\documentclass[runningheads]{llncs}
\usepackage{natbib}
% \usepackage{stmaryrd}
% \usepackage{proof}
% \usepackage{amsmath}
% \usepackage{amssymb}
% \usepackage{color}
% \usepackage{bbm}
% \usepackage[greek,english]{babel}
% \usepackage{ucs}
% \usepackage[utf8x]{inputenc}
% \usepackage{autofe}
\usepackage{agda}
\usepackage{revsymb}
\usepackage{semantic}
\usepackage{graphicx}
\usepackage{url}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{stix}
\setcitestyle{round,aysep={}}

\begin{document}
\title{Programming Language Foundations in Agda}
\author{Philip Wadler}
\authorrunning{P. Wadler}
\institute{University of Edinburgh\\
  \email{wadler@inf.ed.ac.uk}}
\maketitle
%
\begin{abstract}
One of the leading textbooks for formal methods is
\emph{Software Foundations} (SF), written by Benjamin Pierce in
collaboration with others, and based on Coq. After five years using SF
in the classroom, I have come to the conclusion that Coq is not the
best vehicle for this purpose, as too much of the course needs to
focus on learning tactics for proof derivation, to the cost of
learning programming language theory.  Accordingly, I have written a
new textbook, \emph{Programming Language Foundations in Agda} (PLFA).
PLFA covers much of the same ground as SF, although it is not a
slavish imitation.

@@

The textbook is written as a literate Agda script, and can be found here:
\begin{center}
\url{http://plfa.inf.ed.ac.uk}
\end{center}
\keywords{Agda \and Coq \and lambda calculus \and dependent types.}
\end{abstract}

@@

Neat layout of definitions such as that in
Figure~\ref{fig:plfa-progress-2} in Emacs requires a monospaced font
supporting all the necessary characters.  Securing one has proved
tricky. As of this writing, we use FreeMono, but it lacks a few
characters ($\typecolon$ and $\qed$) which are loaded from fonts with a different
width.  Long arrows are necessarily more than a single character wide.
Instead, we compose reduction —→ from an em dash — and an arrow →.
Similarly for reflexive and transitive closure —↠.

@@

\bibliographystyle{plainnat}
%\bibliographystyle{splncsnat.bst}
\bibliography{PLFA}

>>>>

\documentclass[preprint,authoryear]{elsarticle}
%\usepackage{natbib}
\usepackage{agda}
\usepackage{revsymb}
\usepackage{semantic}
\usepackage{graphicx}
\usepackage{url}
\renewcommand\UrlFont{\color{blue}\rmfamily}
\usepackage{stix}
\usepackage{amsmath,amssymb,amsthm}
\newtheorem{theorem}{Theorem}
\usepackage{mathpazo}
\usepackage[mathpazo]{flexisym}

\begin{document}

\title{Programming Language Foundations in Agda}

\author[adr1]{Wen Kokke}
\ead{wen.kokke@ed.ac.uk}
\author[adr2]{Jeremy Siek}
\ead{jsiek@indiana.edu}
\author[adr1]{Philip Wadler\corref{cor1}}
\ead{wadler@inf.ed.ac.uk}
\cortext[cor1]{Corresponding author}

\address[adr1]{University of Edinburgh, 10 Crichton Street, EH8 9AB, Edinburgh}
\address[adr2]{Indiana University, 700 N Woodlawn Ave, Bloomington, IN 47408, USA}

\begin{abstract}
  One of the leading textbooks for formal methods is \emph{Software Foundations} (SF), written by Benjamin Pierce in collaboration with others, and based on Coq. After five years using SF in the classroom, I have come to the conclusion that Coq is not the best vehicle for this purpose, as too much of the course needs to focus on learning tactics for proof derivation, to the cost of learning programming language theory.  Accordingly, I have written a new textbook, \emph{Programming Language Foundations in Agda} (PLFA). PLFA covers much of the same ground as SF, although it is not a slavish imitation.

@@

  The textbook is written as a literate Agda script, and can be found here:
  \begin{center}
    \url{http://plfa.inf.ed.ac.uk}
  \end{center}
\end{abstract}

\begin{keyword}
  Agda \sep Coq \sep lambda calculus \sep dependent types.  
\end{keyword}

\maketitle

@@

Neat layout of definitions such as that in
Figure~\ref{fig:plfa-progress-2} in Emacs requires a monospaced font
supporting all the necessary characters.  Securing one has proved
tricky. As of this writing, we use FreeMono, but it lacks a few
characters ($\typecolon$ and $\qedsymbol$) which are loaded from fonts with a different
width.  Long arrows are necessarily more than a single character wide.
Instead, we compose reduction —→ from an em dash — and an arrow →.
Similarly for reflexive and transitive closure —↠.

@@

\section*{References}

\bibliographystyle{elsarticle-harv}
\bibliography{PLFA}
